Stateless Model Checking with Data-Race Preemption Points

### 2016-08-23 oopsla-16/overview.tex
take care of some TODO CAMREADies
fix more TODO CAMREADies
oopsla: i don't think i'm actually going to fix figure 2

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{trees-v2-squashed.pdf}
	\caption{Iterative Deepening example.
		The minimal state space (A) includes only voluntary thread switches, such as {\tt yield()}. %or {\tt cond\_wait()}.
		Multiple further tests can be run: preempting on calls to {\tt mutex\_lock} alone (B), {\tt mutex\_unlock} alone (C), or both together (D).
Each option increases the state space size unpredictably, so multiple state spaces should be tested in parallel.
Estimation techniques~\cite{estimation} inform which state spaces to prioritize.
}
	\label{fig:id}
\end{figure}

The checker defines the granularity of thread interleavings by the {\em preemption points} it uses to switch threads.
Most model checkers \cite{chess,dbug-ssv} choose synchronization/thread library API boundaries for these points;
in our example program, these would be lines 1, 4, and 7.
Figure~\ref{fig:id} shows several possible resulting state spaces.
The approach of prior work is to enable all preemption points simultaneously, i.e., to test only the state space denoted (D).

@@

\revisionx{Being dynamic analyses, both HB and Limited HB may suffer false negatives when a racy access pair is not executed at all in a specific interleaving.
Limited HB offers the advantage of identifying a potential race as long as the access pair is observed under any interleaving,
rather than requiring the accesses to be adjacent in time, as HB would.}
While stand-alone data-race analyses must avoid inundating the user with false alarms \cite{racerx},
%However,
we incorporate data-race analysis in an internal feedback loop,
using model checking to automatically test each potential race
and report only directly observed failures to the user.
%Our convergence theorem requires identifying all potential data-races to provide total verification (\sect{\ref{sec:totalverif}})
%% TODO CAMREADY: cite our soundness proofs tech report in this paragraph as well
%Hence, we employ Limited HB in this paper},
%accepting some overhead from false positives for the sake of total verification (\sect{\ref{sec:totalverif}}).
\revisionx{Hence, we can accept some overhead from Limited HB's false positives for the sake of finding data-race candidates more quickly.
In \sect{\ref{sec:eval}} we will evaluate how HB and Limited HB each influence \quicksand's bug-finding and verification speed.
}

>>>>

%\begin{figure}[t]
%	\begin{tabular}{c}
%	\includegraphics[width=0.42\textwidth]{tree-maximal-only.pdf}
%	\end{tabular}
%	\caption{\revisionz{The state space of possible interleavings is represented as a tree,
%	which stateless model checkers test exhaustively.
%	This state space arises when preempting on synchronization APIs used by the program in Figure~\ref{fig:example};
%	other state spaces are possible with more, or fewer, preemption points.}}
%	\label{fig:tree-maximal}
%\end{figure}

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{trees.pdf}
	\caption{Iterative Deepening example.
		The minimal state space (a) includes only voluntary thread switches, such as {\tt yield()}. %or {\tt cond\_wait()}.
		Multiple further tests can be run: preempting on calls to {\tt mutex\_lock} alone (b), {\tt mutex\_unlock} alone (c), or both together (d).
Each option increases the state space size unpredictably, so multiple state spaces should be tested in parallel.
Estimation techniques~\cite{estimation} inform which state spaces to prioritize.
}
	\label{fig:id}
\end{figure}

The checker defines the granularity of thread interleavings by the {\em preemption points} it uses to switch threads.
Most model checkers \cite{chess,dbug-ssv} choose synchronization/thread library API boundaries for these points;
in our example program, these would be lines 1, 4, and 7.
Figure~\ref{fig:id} shows several possible resulting state spaces.
The approach of prior work is to enable all preemption points simultaneously, i.e., to test only the state space denoted (d).

@@

\revisionx{Being dynamic analyses, both HB and Limited HB may suffer false negatives when a racy access pair is not executed at all in a specific interleaving.
Limited HB offers the advantage of identifying a potential race as long as the access pair is observed under any interleaving,
rather than requiring the accesses to be adjacent in time, as HB would.}
While stand-alone data-race analyses must avoid inundating the user with false alarms \cite{racerx},
%However,
we incorporate data-race analysis in an internal feedback loop,
using model checking to automatically test each potential race
and report only directly observed failures to the user.
%Our convergence theorem requires identifying all potential data-races to provide total verification (\sect{\ref{sec:totalverif}})
%Hence, we employ Limited HB in this paper},
%accepting some overhead from false positives for the sake of total verification (\sect{\ref{sec:totalverif}}).
\revisionx{Hence, we can accept some overhead from Limited HB's false positives for the sake of finding data-race candidates more quickly.
In \sect{\ref{sec:eval}} we will evaluate how HB and Limited HB each influence \quicksand's bug-finding and verification speed.
}
